### 2023-02-08 materials-lisa/notes/GPP-AIness-notes.tex
added some notes and graphs

% \section{Questions} % (fold)
% 	\begin{itemize}
% 		\item Were the questions for projection / at-issueness diagnostics asked in randomized order?
% 		\item What were the thoughts on arousal? How would this come into play? Is the idea that it would interact with the QUD?
% 		\item How exactly are the pilots different from the main experiments?
% 	\end{itemize}

% % section questions (end)

@@

	\subsection{3q---Question embedding, yes but not $c^\prime$ (+ acceptability rating)}
		\ex. \a. \textbf{Christopher:} Did Cole discover that Julian dances salsa?
				\b. \textbf{Sandy:} Yes, Julian dances salsa.
				\z.
			\z.

@@

\pagebreak
\section{Some more notes} % (fold)

>>>>

@@

	\subsection{3q---Question embedding, yes but not $c^\prime$ (+ acceptability rating)}
		\ex. \a. \textbf{Christopher:} Did Cole discover that Julian dances salsa?
				\b. \textbf{Sandy:} Yes, but Cole didn't discover that.
				\z.
			\z.

@@

\pagebreak
\section{Experiments with Conditionals} % (fold)
	\subsection{1c---Conditional embedding,  are you sure?, assent + assertion of complement + Q-A judgment}

		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Are you sure?
			\b. \textbf{Christopher:} Yes, I'm sure that Julian dances Salsa.
			\z.
		\z.

		\ex. The two follow-ups will be acceptable, (only) if:
			\a. \textbf{At-issueness:}\\ \label{cond:ai}
				Christophers utterance was \lq about\rq\ whether Julian dances Salsa, \textbf{and}
			\b. \textbf{Commitment:}\\ \label{cond:commit}
				Christopher is committed that Julian dances Salsa
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[]{figures/c1-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. c1}
			\label{fig:c1-corr}
		\end{figure}

		Three points are relevant here:
		\begin{itemize}
			\item Regarding at-issueness:\\
				We can assume that any content from a sentence-initial conditional antecedent, is hard to interpret as at-issue. The discourse has already progressed, and the sentence-final main clause is more likely to determine the relevant set of alternatives for the subsequent discourse. (Maybe it is worth taking into account a more dynamic view of at-issueness. Look clause-by-clause; Adressing the previous QUD vs determining relevant set of alternatives for subsequent discourse)
			\item Regarding speaker commitment:\\
				Based on literal content, the speaker may or may not be committed to Julian dancing salsa.
			\item Regarding interaction of the two:
			\begin{itemize}
				\item If content is at issue, it will be targeted by entailment cancelling operator, and now the speaker is not committed to the content. In that case, the follow-up is unacceptable by \ref{cond:commit}.
				\item If content is not at-issue, it will project, and the speaker is committed. Now, however, the follow-up is unacceptable by \ref{cond:ai}.
			\end{itemize}

	% subsection 1c_conditional_ (end)

	\subsection{2c---Conditional embedding,  yes, that's true+complement diagnostic (+ acceptability rating)} 
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Yes, that’s true, Julian dances salsa.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[]{figures/c2-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. c2}
			\label{fig:c2-corr}
		\end{figure}

	% subsection 2c_ (end)

	\subsection{3c---Conditional embedding, yes, that's true + negation of main clause (+ acceptability rating)}
		\ex. \a. \textbf{Christopher:} If Cole discovered that Julian dances salsa, Logan will be joyful.
			\b. \textbf{Sandy:} Yes, that’s true, but Cole didn't discover it.
			\z.
		\z.

		\begin{figure}[h]
			\centering
			\includegraphics[]{figures/c3-correl.pdf}
			\caption{Mean not-at-issueness ratings vs mean certainty ratings by predicate, Exp. c3}
			\label{fig:c3-corr}
		\end{figure}

	% subsection 3c_conc (end)

% section experiments_with_conditionals (end)

\section{Some more notes} % (fold)
